# Yelp BizOps Analytics Dashboard 


## Getting Started

These instructions allow you to replicate our dashboard on your own local machine for development and testing purposes. The initial set-up requires that you run the install Apache Drill in embedded mode.

It's strongly recommend to check out [this link](https://drill.apache.org/docs/drill-in-10-minutes/) to get drill properly installed & running.  

Apache Drill Embedded Mode Prerequisites:
* Linux, Mac OS X, and Windows: Oracle JDK version 7 or version 8 if running Drill 1.6 or later [more](https://drill.apache.org/docs/drill-in-10-minutes/)

Install Drill on Linux or MAC OS X

Complete the following steps to install Drill:

In a terminal window, change to the directory where you want to install Drill.

Download the latest version of Apache Drill [here](http://apache.mirrors.hoobly.com/drill/drill-1.10.0/apache-drill-1.10.0.tar.gz) or from the [Apache Drill mirror](http://www.apache.org/dyn/closer.cgi/drill/drill-1.10.0/apache-drill-1.10.0.tar.gz) site with the command appropriate for your system:
```{r}
wget 'http://apache.mirrors.hoobly.com/drill/drill-1.10.0/apache-drill-1.10.0.tar.gz'

curl -o apache-drill-1.10.0.tar.gz 'http://apache.mirrors.hoobly.com/drill/drill-1.10.0/apache-drill-1.10.0.tar.gz'
```

Copy the downloaded file to the directory where you want to install Drill.
Extract the contents of the Drill .tar.gz file. Use sudo if necessary:


```{r}
tar -xvzf <.tar.gz file name>
```


### Other Prerequisites

* [RStudio](http://www.dropwizard.io/1.0.2/docs/) - IDE for R
* [Flexdashboards](https://maven.apache.org/) - Easy, flexible dashboards using the Shiny apps framework
* [Apache Drill](https://rometools.github.io/rome/) - Used to connect R with a variety of backend NoSQL database
* [Sergeant]() - Tools to Transform and Query Data with Apache 'Drill'

### Installation(s)

```{r}

```




## Authors

* **Alec Miller**
* **Paige Tuchner** 

## Acknowledgments

* Hat tip to: 

